My title

### 2024-03-14 paper/paper.qmd
update discussion

#### Read in necessary data and model ####
cleaned_data_post_strat <-read_csv(file = here("data/analysis_data/usa_00002_cleaned.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/analysis_data/ns20191003_cleaned.csv"), show_col_types = FALSE)

survey_model <- readRDS(file = here("models/consider_trump.rds"))
predicton_model <- readRDS(file = here("models/census_data_with_predictions.rds"))
```

>>>>

#### Read in necessary data and model ####
cleaned_data_post_strat <-read_csv(file = here("data/analysis_data/usa_00002_cleaned.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/analysis_data/ns20191003_cleaned.csv"), show_col_types = FALSE)
```
